ICBEdataset figure Metro Maps

### 2022-01-27 replication_paper/rmd/ICBEdataset_figure_metro_maps.Rmd
heresy

    #Units
  units <-   codings_wide_agreed_subset %>% dplyr::select(sent=final_event_ordering, do_actor_a, interact_units) %>% na.omit()  %>% 
              mutate(interact_units = strsplit(as.character(interact_units), ";")) %>% unnest(interact_units) %>%
              mutate(do_actor_a = strsplit(as.character(do_actor_a), ";")) %>% unnest(do_actor_a) %>%
              mutate(IMAGE=paste0(here::here, '/replication_paper/figures/metro_plots/symbols/',interact_units,'.png')) %>%
              mutate(actor_sent= do_actor_a %>% paste0("_", str_pad(sent, 2, pad = "0") )) %>%
              left_join(codings_wide_agreed_subset_nodes %>% dplyr::select(actor_sent, x, y) ) %>%
              dplyr::select(-sent, -do_actor_a) %>% distinct() %>% 
              arrange(actor_sent, interact_units) %>%
              group_by(actor_sent) %>%
                mutate(units_count=n()) %>%
                mutate(middle=units_count/2) %>%
                mutate(units_number=row_number()) %>%
                mutate(offeset=(middle-units_number)*10)

>>>>

    #Units
  units <-   codings_wide_agreed_subset %>% dplyr::select(sent=final_event_ordering, do_actor_a, interact_units) %>% na.omit()  %>% 
              mutate(interact_units = strsplit(as.character(interact_units), ";")) %>% unnest(interact_units) %>%
              mutate(do_actor_a = strsplit(as.character(do_actor_a), ";")) %>% unnest(do_actor_a) %>%
              mutate(IMAGE=paste0(here::here(), '/replication_paper/figures/metro_plots/symbols/',interact_units,'.png')) %>%
              mutate(actor_sent= do_actor_a %>% paste0("_", str_pad(sent, 2, pad = "0") )) %>%
              left_join(codings_wide_agreed_subset_nodes %>% dplyr::select(actor_sent, x, y) ) %>%
              dplyr::select(-sent, -do_actor_a) %>% distinct() %>% 
              arrange(actor_sent, interact_units) %>%
              group_by(actor_sent) %>%
                mutate(units_count=n()) %>%
                mutate(middle=units_count/2) %>%
                mutate(units_number=row_number()) %>%
                mutate(offeset=(middle-units_number)*10)
